Creation of a DRN shapefile with associated capacities

### 2022-03-17 R/Core_code/DRN_operations/2_New_hdrn.Rmd
repo update

---
title: "Creation of the new HDRN shapefile with capacities associated"
author: "Paolo Colombo"
date: "26/4/2021"
output: html_document
---

@@

```{r libraries}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis")

source("Libraries.R")
source("Functions.R")
```

@@

```{r}
setwd("C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data")

global_water<-readOGR(dsn = "./Global_surface_water/shape/cut_merged.shp")
```

@@

```{r}
path<-"C:/Thesis_fortran/WASA/shapefile/Banabuiu"
main_resI<-st_read(paste0(path,"/mainreservoirsI_cut_ref.shp"))
main_resII<-st_read(paste0(path,"/mainreservoirsII_cut_ref.shp"))

threshold<-min(main_resI$AREA)
glob_wat_cut<-global_water[which(global_water$area_geom < threshold),]

>>>>

---
title: "Creation of a DRN shapefile with associated capacities"
author: "Paolo Colombo"
date: "26/4/2021"
output: html_document
---

@@

```{r libraries}
setwd("C:/Directory_thesis_codes")

source("./R/Libraries/Libraries.R")
source("./R/Libraries/Functions.R")
```

@@

```{r}
global_water <- readOGR(dsn = "./Data/DRN/Global_surface_water/cut_merged.shp")
```

@@

```{r}
path <- "C:/Thesis_fortran/WASA/shapefile/Banabuiu"
main_resI <- st_read(paste0(path, "/mainreservoirsI_cut_ref.shp"))
main_resII <- st_read(paste0(path, "/mainreservoirsII_cut_ref.shp"))

threshold <- min(main_resI$AREA)
glob_wat_cut <- global_water[which(global_water$area_geom < threshold),]
